### 2011-08-14 trunk/docs/Bibliografia/bib.tex
Se corrige cap tiempos, y ensayos.

%Application Notes
\bibitem{ACD} Antenna Circuit Design for RFID Applications, AN710.
\bibitem{ADN} HF Antenna Design Notes, Literature Number: 11-08-26-003.
\bibitem{HFACB} HF Antenna Cook Book, Lit. Number 11-08-26-001.
\bibitem{MRICF} Micore Reader IC Family; Directly Matched Antenna Design, Rev. 2.05, 10 May 2006.
\bibitem{RFIDPA} Mifare®(14443A) 13,56 MHz RFID Proximity Antennas, Application Note.
\bibitem{} MIFARE Type Identification Procedure; AN10833 Rev. 3.1 — 07 July 2009.
\bibitem{} MIFARE ISO/IEC 14443 PICC Selection; AN10834 Rev. 3.0 — 26 June 2009.
\bibitem{} MIFARE Classic Commands; AN10856 Rev. 1.0 — 31 July 2009.
\bibitem{} MIFARE and handling of UIDs; AN10927 Rev. 2.0 — 01 September 2010.
\bibitem{} Mainstream contactless smart card IC for fast and easy; MF1S5009 Rev. 3 — 27 July 2010.
\bibitem{} MIFARE Standard Card IC MF1 IC S50 Functional Specification; Revision 5.1 May 2001.

@@

%CT/API cap-6
\bibitem{ctapi} Application Independent CardTerminal Application Programming Interface for ICC Applications; 
Deutsche Telekom AG / PZ Telesec, GMD - Forschungszentrum Informationstechnik GmbH, TÜV Informationstechnik GmbH, TELETRUST Deutschland e.V., 30.10.1996.

%CT/BCS cap-6
\bibitem{ctbcs} Application independent CardTerminal Basic Command Set for ICC applications; 
TeleTrusT Deutschland e.V., GMD Forschungszentrum Informationstechnik GmbH, Version 0.9, 28.07.1995.

%IFDhandler
\bibitem{ifdhandler} IFDHandler 3.0 MUSCLE PC/SC IFD Driver API; David Corcoran \& Ludovic Rousseau, July 28, 2004.

%Libros
\bibitem{KiCad} Diseño y desarrollo de circuitos impresos con KiCad, Miguel Pareja Aparicio, 2010, ISBN: 978-84-937769-1-6.

@@

%LINKS

\bibitem{OpenPCD} OpenPCD, http://www.openpcd.org/, agosto 2011.
\bibitem{usb4all} USB4ALL, http://www.fing.edu.uy/inco/grupos/mina/pGrado/pgusb/main.php, agosto 2011.
\bibitem{librfid} librfid, http://openmrtd.org/projects/librfid/, agosto 2011.
\bibitem{9G20} GES9G20, http://www.glomationinc.com/product\_9G20.html, agosto 2011.
\bibitem{Hawk} Hawkboard, http://www.hawkboard.org/, agosto 2011.
\bibitem{Beagle} Beagleboard, http://beagleboard.org/, agosto 2011.
\bibitem{foroBb} Foro de Beagleboard, https://groups.google.com/forum/\#!forum/beagleboard, agosto 2011.
\bibitem{OE-Bb} Openembedded-Bitbake, http://wiki.openembedded.net/index.php/BitBake\_\%28dev\%29, agosto 2011.
\bibitem{KiCad} KiCad, http://www.lis.inpg.fr/realise\_au\_lis/kicad/, agosto 2011.
\bibitem{gEDA} gEDA, http://www.gpleda.org/index.html, agosto 2011.
\bibitem{Proxmark} Proxmark, http://www.proxmark.org/proxmark, agosto 2011.
\bibitem{Angs} Angström, http://www.angstrom-distribution.org/, agosto 2011.
\bibitem{Angs_MLO} MLO, http://www.angstrom-distribution.org/demo/beagleboard/MLO/, agosto 2011.
\bibitem{Narc} Narcissus, http://narcissus.angstrom-distribution.org/, agosto 2011.
\bibitem{termios} termios, http://pubs.opengroup.org/onlinepubs/007908799/xsh/termios.h.html, agosto 2011.
\bibitem{linuxBoot} Proceso de booteo de linux, http://www.ibm.com/developerworks/linux/library/l-linuxboot/index.html, agosto 2011.
\bibitem{Make} Make, http://es.wikipedia.org/wiki/Make, agosto 2011.
\bibitem{DDD} DDD, http://www.gnu.org/s/ddd/, agosto 2011.
\bibitem{gpio} GPIO, http://www.avrfreaks.net/wiki/index.php/Documentation:Linux/GPIO\#Interfaces\_explained, agosto 2011.
\bibitem{gpioK} Kernel GPIO, http://kernel.org/doc/Documentation/gpio.txt, agosto 2011.

\bibitem{conf_SDK} Configuración SDK, http://www.electronsonradio.com/2011/04/intro-to-basic-cross-compiling-for-the-beagleboard/, agosto 2011.

@@

%links sobre puerto serial y comandos linux necesarios para entender código
\bibitem{} http://www.easysw.com/~mike/serial/serial.html
\bibitem{} http://linux.die.net/man/3/fd\_set
\bibitem{} http://linux.die.net/man/2/select\_tut
\bibitem{} http://www.iearobotics.com/wiki/index.php?title=Tutorial:Puerto\_serie\_en\_Linux
\bibitem{} http://es.tldp.org/COMO-INSFLUG/COMOs/Programacion-Serie-Como/Programacion-Serie-Como-3.html
\bibitem{} http://www.rastersoft.com/articulo/pserie.html
\bibitem{} http://www.faqs.org/docs/Linux-mini/IO-Port-Programming.html
\bibitem{} http://tldp.org/HOWTO/IO-Port-Programming-2.html

%links sobre pcsc
\bibitem{pcsclite} PCSC-Lite, http://pcsclite.alioth.debian.org/
\bibitem{pcsclite_esp} PCSC Workgroup, http://www.pcscworkgroup.com/
\bibitem{pcsc/ccid_down} Descargas PCSC-Lite, https://alioth.debian.org/frs/?group\_id=30105
\bibitem{pcsctools_down} http://ludovic.rousseau.free.fr/softwares/pcsc-tools/
\bibitem{} http://ludovicrousseau.blogspot.com/2011/04/libccid-and-usb-selective-suspend.html
\bibitem{} http://readthedocs.org/docs/pvdevtools\_doc/en/latest/index.html
\bibitem{} http://www.springcard.com/support/pcsclite.html

\end{thebibliography}

>>>>

%Application Notes
\bibitem{ACD} Antenna Circuit Design for RFID Applications, AN710.
\bibitem{ADN} HF Antenna Design Notes, Literature Number: 11-08-26-003.
\bibitem{HFACB} HF Antenna Cook Book, Lit. Number 11-08-26-001.
\bibitem{MRICF} Micore Reader IC Family; Directly Matched Antenna Design, Rev. 2.05, 10 May 2006.
\bibitem{RFIDPA} Mifare®(14443A) 13,56 MHz RFID Proximity Antennas, Application Note.

\bibitem{} MIFARE Type Identification Procedure; AN10833 Rev. 3.1 — 07 July 2009.
\bibitem{} MIFARE ISO/IEC 14443 PICC Selection; AN10834 Rev. 3.0 — 26 June 2009.
\bibitem{} MIFARE Classic Commands; AN10856 Rev. 1.0 — 31 July 2009.
\bibitem{} MIFARE and handling of UIDs; AN10927 Rev. 2.0 — 01 September 2010.
\bibitem{} Mainstream contactless smart card IC for fast and easy; MF1S5009 Rev. 3 — 27 July 2010.
\bibitem{} MIFARE Standard Card IC MF1 IC S50 Functional Specification; Revision 5.1 May 2001.

@@

%Angström
\bibitem{AngManual} Angström Manual - Embedded Power -, Luca Merciadri and Kooi Koën, 29 June 2010.

%CT/API cap-6
\bibitem{ctapi} Application Independent CardTerminal Application Programming Interface for ICC Applications; 
Deutsche Telekom AG / PZ Telesec, GMD - Forschungszentrum Informationstechnik GmbH, TÜV Informationstechnik GmbH, TELETRUST Deutschland e.V., 30.10.1996.
%CT/BCS cap-6
\bibitem{ctbcs} Application independent CardTerminal Basic Command Set for ICC applications; 
TeleTrusT Deutschland e.V., GMD Forschungszentrum Informationstechnik GmbH, Version 0.9, 28.07.1995.
%IFDhandler
\bibitem{ifdhandler} IFDHandler 3.0 MUSCLE PC/SC IFD Driver API; David Corcoran \& Ludovic Rousseau, July 28, 2004.

%Libros
\bibitem{KiCad} Diseño y desarrollo de circuitos impresos con KiCad, Miguel Pareja Aparicio, 2010, ISBN: 978-84-937769-1-6.
\bibitem{} El lenguaje de programación C, Brian W. Kernighan y Dennis M. Ritchie, 1991, ISBN: 968-880-205-0.

@@

%LINKS
\bibitem{OpenPCD} OpenPCD, http://www.openpcd.org/, agosto 2011.
\bibitem{librfid} librfid, http://openmrtd.org/projects/librfid/, agosto 2011.
\bibitem{9G20} GES9G20, http://www.glomationinc.com/product\_9G20.html, agosto 2011.
\bibitem{Hawk} Hawkboard, http://www.hawkboard.org/, agosto 2011.
\bibitem{Beagle} Página oficial Beagleboard, http://beagleboard.org/, agosto 2011.
\bibitem{foroBb} Foro de Beagleboard, https://groups.google.com/forum/\#!forum/beagleboard, agosto 2011.
\bibitem{consumo1} Consumo de Beagleboard, http://elinux.org/BeagleBoardFAQ\#Power\_usage, \\
agosto 2011.
\bibitem{consumo2} Consumo de Beagleboard, http://www.h-online.com/news/forum/S-Power-\\
consumption-under-2W/forum-110345/msg-14369911/read/, agosto 2011.
\bibitem{OE-Bb} Openembedded-Bitbake, http://wiki.openembedded.net/index.php/BitBake\_\%28
dev\%29, agosto 2011.
\bibitem{KiCad} KiCad, http://www.lis.inpg.fr/realise\_au\_lis/kicad/, agosto 2011.
\bibitem{gEDA} gEDA, http://www.gpleda.org/index.html, agosto 2011.
\bibitem{Proxmark} Proxmark, http://www.proxmark.org/proxmark, agosto 2011.
\bibitem{Angs} Angström, http://www.angstrom-distribution.org/, agosto 2011.
\bibitem{Angs_MLO} MLO, http://www.angstrom-distribution.org/demo/beagleboard/MLO/, agosto 2011.
\bibitem{Narc} Narcissus, http://narcissus.angstrom-distribution.org/, agosto 2011.
\bibitem{termios} termios, http://pubs.opengroup.org/onlinepubs/007908799/xsh/termios.h.html, agosto 2011.
\bibitem{linuxBoot} Proceso de booteo de linux, http://www.ibm.com/developerworks/linux/library/
l-linuxboot/index.html, agosto 2011.
\bibitem{Make} Make, http://es.wikipedia.org/wiki/Make, agosto 2011.
\bibitem{DDD} DDD, http://www.gnu.org/s/ddd/, agosto 2011.
\bibitem{gpio} GPIO, http://www.avrfreaks.net/wiki/index.php/Documentation:Linux/GPIO\#
Interfaces\_explained, agosto 2011.
\bibitem{gpioK} Kernel GPIO, http://kernel.org/doc/Documentation/gpio.txt, agosto 2011.
\bibitem{conf_SDK} Configuración SDK, http://www.electronsonradio.com/2011/04/intro-to-basic-cross-compiling-for-the-beagleboard/, agosto 2011.
\bibitem{mina} Grupo mina - INCO, http://www.fing.edu.uy/inco/grupos/mina/, agosto 2011.
\bibitem{lcd4linux} LCD4Linux, http://ssl.bulix.org/projects/lcd4linux/, agosto 2011.

%links Daniel
\bibitem{} Beagleboards beginners, https://groups.google.com/forum/\#!forum/beagleboard, agosto 2011.

\bibitem{} Desarrollo en Beagleboard, http://members.cox.net/ebrombaugh1/embedded/
beagle/index.html, agosto 2011.

\bibitem{} Wiki Beagleboard, http://code.google.com/p/beagleboard/w/list, agosto 2011.

\bibitem{} NAND de la Beagleboard, http://elinux.org/BeagleBoardNAND, agosto 2011.

\bibitem{} Croscompilación en Beagleboard, http://garrenblog.blogspot.com/2008/10/adven
tures-in-beagleboard-land-compiler.html, agosto 2011.

\bibitem{} Primeros pasos Beagleboard, http://www.mipixel.com/electronica/beagleboard, agosto 2011.

\bibitem{} Arranque de Linux en la Beagleboard, http://www.ibm.com/developerworks/libra
ry/l-beagle-board/index.html, agosto 2011.

\bibitem{} Internet en Beagleboard, http://thoughtshubham.blogspot.com/2010/03/internet-over-usb-otg-on-beagleboard.html, agosto 2011.

\bibitem{} OpenEmbedded en Ubuntu 10.04, http://maltanar.blogspot.com/2010/05/open
embedded-on-ubuntu-1004.html, agosto 2011.

\bibitem{} Solución de problemas con Beagleboard, http://www.electronsonradio.com/cate
gory/bb/, agosto 2011.

\bibitem{} Foro Beagleboard - Testeo SPI, http://groups.google.com/group/beagleboard/
browse\_thread/thread/d6a4e0703033cada\%7CSPI, agosto 2011.

\bibitem{} SPI en Beagleboard, http://elinux.org/BeagleBoard/SPI, agosto 2011.

\bibitem{} Parche SPI en Beagleboard con kernel 2.6.32, http://elinux.org/BeagleBoard/
SPIPatch-2.6.32, agosto 2011.

\bibitem{} Foro Beagleboard – SPI, https://groups.google.com/forum/\#!topic/beagleboard/
p7Ua8jmILkM, agosto 2011.

\bibitem{} Foro Beagleboard - Configuración SPI, https://groups.google.com/forum/\#!topic/
beagleboard/QpiPDhTbDwE, agosto 2011.

\bibitem{} Foro Beagleboard - Configuración SPI, https://groups.google.com/forum/\#!topic/
beagleboard/3v3qsRQNQzA, agosto 2011.

\bibitem{} Foro Beagleboard - Aplicar parche SPI, https://groups.google.com/forum/
\#!searchin/beagleboard/\%22bitbake\$20-c\$20rebuild\%22/beagleboard/TF6TCJx
XL1Y/joHWHlxiPZEJ, agosto 2011.

\bibitem{} Foro Beagleboard - SPI en Beagleboard, https://groups.google.com/forum/
\#!searchin/beagleboard/applying\$20patches/beagleboard/s340Ss-GoJU/
KAeSfH8vqb8J, agosto 2011.

\bibitem{} Foro Beagleboard - Problemas con SPI, https://groups.google.com/forum/?show
\_docid=9db5bcf44392d4a0\#!topic/beagleboard/MgzrowFy-6U, agosto 2011.

\bibitem{} Foro Beagleboard - Construyendo un kernel y habilitar SPI, https://groups.
google.com/forum/\#!topic/beagleboard/XrMz-9Byum0, agosto 2011.

\bibitem{} Foro Beagleboard - SPI en Beagleboard, https://groups.google.com/forum/
\#!topic/beagleboard/s340Ss-GoJU, agosto 2011.

\bibitem{} Foro Beagleboard - Compilación de kernel, https://groups.google.com/forum/
?pli=1\#!searchin/beagleboard/mkimage/beagleboard/Od\_tCEHwUvk/DxoPO8Y
v9t0J, agosto 2011.

\bibitem{} Foro Beagleboard - Problemas construyendo uImage, https://groups.google.com/
forum/?pli=1\#!msg/beagleboard/MDxilRJKIIQ/r0RVzZdIdYsJ, agosto 2011.

\bibitem{} Foro Beagleboard - Sobre las versiones generadas de uImage, https://groups.
google.com/forum/\#!topic/beagleboard/DR-ruujKu9U, agosto 2011.

\bibitem{} Foro Beagleboard - Aplicar parche al kernel linux, https://groups.google.com/\\
forum/\#!searchin/beagleboard/applying\$20patches/beagleboard/bAjYSVKAyAM/
jCTXlbfn40wJ, agosto 2011.

\bibitem{} Openmbedded, http://www.openembedded.org/index.php/Main\_Page, agosto 2011.

\bibitem{} OpenEmbedded , uso, http://www.uv-ac.de/openembedded/, agosto 2011.

\bibitem{} Foro Beagleboard - configuración de kernel con OpenEmbedded, https://groups.
google.com/forum/\#!msg/beagleboard/UlL4e0\_O\_UE/\_NefIFsj7pkJ, agosto 2011.

\bibitem{} Bitbake, tutorial, http://www.gumstix.org/software-development/open-embedded
/160-bitbake-tutorial.html, agosto 2011.

\bibitem{} Bitbake, tutorial, http://bitbake.berlios.de/manual/, agosto 2011.

\bibitem{} Foro Beagleboard - OpenEmbedded/Bitbake, como forzar regeneración de \\
uImage, https://groups.google.com/forum/?pli=1\#!searchin/beagleboard/uimage/
beagleboard/FibI\_LXNVGk/mNHp6ZPNOAYJ, agosto 2011.

\bibitem{} Foro Beagleboard - U-boot, fuentes, https://groups.google.com/forum/\#!searchin/
beagleboard/u-boot\$20source/beagleboard/XD82Fd54ABg/xCUaE5W\_OwQJ, agosto 2011.

\bibitem{} Beagleboard, desarrollo de software, http://wh1t3s.com/tag/beagleboard/, agosto 2011.

\bibitem{} Foro Beagleboard - Línea de 1.8V en el bloque de expansión, https://groups.\\
google.com/forum/\#!topic/beagleboard/00urlSRNrXA, agosto 2011.

\bibitem{} PinMux en el bloque de expansión, http://elinux.org/BeagleBoardPinMux, agosto 2011.

\bibitem{} Guía de programación Serial, http://www.easysw.com/$\sim$mike/serial/serial.html, agosto 2011.

\bibitem{} Chequear y utilizar puertos seriales bajo Linux, http://www.cyberciti.biz/faq/find-out-linux-serial-ports-with-setserial/, agosto 2011.

\bibitem{} Programación Serial, http://tldp.org/HOWTO/Serial-Programming-HOWTO/\\
x115.html, agosto 2011.

\bibitem{} Programación Serial, http://www.linux.com/learn/docs/ldp/745-Serial-Progra\\
mming-HOWTO, agosto 2011.

\bibitem{} Interfaz GPIO, http://www.avrfreaks.net/wiki/index.php/Documentation:Linux/GPIO, agosto 2011.

\bibitem{} Encendido y apagado de pines de la Beagleboard, http://blog.makezine.com/\\
archive/2009/02/blinking-leds-with-the-beagle-board.html?CMP=OTC-0D6B48984890, agosto 2011.

\bibitem{} Uso de diff y patch, http://www.linuxtutorialblog.com/post/introduction-using-diff-and-patch-tutorial, agosto 2011.

\bibitem{} CodeSourcery 2009q3-67, http://www.codesourcery.com/sgpp/lite/arm/portal/\\
release1039, agosto 2011.

\bibitem{} Librfid, instalación, http://wiki.yobi.be/wiki/RFID\#librfid, agosto 2011.

\bibitem{} Proyectos con Beagleboard, http://www.hy-research.com/projects.html, agosto 2011.

%fin de links Daniel

%links sobre pcsc
\bibitem{pcsclite} PCSC-Lite, http://pcsclite.alioth.debian.org/
\bibitem{pcsclite_esp} PCSC Workgroup, http://www.pcscworkgroup.com/
\bibitem{pcsc/ccid_down} Descargas PCSC-Lite, https://alioth.debian.org/frs/?group\_id=30105
\bibitem{pcsctools_down} http://ludovic.rousseau.free.fr/softwares/pcsc-tools/

\bibitem{} http://ludovicrousseau.blogspot.com/2011/04/libccid-and-usb-selective-suspend.html
\bibitem{} http://readthedocs.org/docs/pvdevtools\_doc/en/latest/index.html
\bibitem{} http://www.springcard.com/support/pcsclite.html

@@

%links sobre puerto serial y comandos linux necesarios para entender código
\bibitem{} http://www.easysw.com/~mike/serial/serial.html
\bibitem{} http://linux.die.net/man/3/fd\_set
\bibitem{} http://linux.die.net/man/2/select\_tut
\bibitem{} http://www.iearobotics.com/wiki/index.php?title=Tutorial:Puerto\_serie\_en\_Linux
\bibitem{} http://es.tldp.org/COMO-INSFLUG/COMOs/Programacion-Serie-Como/Programacion-Serie-Como-3.html
\bibitem{} http://www.rastersoft.com/articulo/pserie.html
\bibitem{} http://www.faqs.org/docs/Linux-mini/IO-Port-Programming.html
\bibitem{} http://tldp.org/HOWTO/IO-Port-Programming-2.html
\end{thebibliography}
